\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-26 paper.qmd
Added description for starting point of hexagonal grid

According to @Dan2023, the hexagonal binning is done by tessellating the $xy$ plane over the set (range($x$), range($y$)) (see @fig-scurveshifthexgridsexp (b)). In that case, bin centroids are defined as shown in @fig-scurveshifthexgridsexp (a) with gray colour. Rather than sticking to the typical hexagonal grid, introducing a meaningful shift in both the x and y directions presents an opportunity for an improved 2D model. Therefore, investigating this shift in the hexagonal grid is an important parameter to consider.

As shown in @fig-scurveshifthexgrids, the shifting influences the distribution of points and number of non-empty bins, impacting the resulting 2D model. According to @fig-diagnosticpltScurvehexbins, the 2D model with a total of $144$ bins applied to S-curve UMAP data does not require any shifting because the lowest MSE occurs when no shift is introduced.

>>>>

Hexagonal binning involves tessellating the $xy$ plane over the set defined by the range of $x$ and $y$ [@Dan2023]. Therefore, the starting point of the hexagonal grid is important parameter to consider. Having different starting point results in shifting the hexagonal grid and bin centroids (see @fig-scurveshifthexgridsexp). With a specific total number of bins (which corresponds to a specific range along the x and y axes), it's essential to explore how different starting points affect the model's performance (see @fig-mseScurvestartpoint). This is because different starting points result in varying distributions of non-empty bins (see @fig-scurveshifthexgrids), impacting the model.

### 2024-03-26 paper.tex
Added description for starting point of hexagonal grid

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, enhanced, frame hidden, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

According to \citet{Dan2023}, the hexagonal binning is done by
tessellating the \(xy\) plane over the set (range(\(x\)), range(\(y\)))
(see Figure~\ref{fig-scurveshifthexgridsexp} (b)). In that case, bin
centroids are defined as shown in
Figure~\ref{fig-scurveshifthexgridsexp} (a) with gray colour. Rather
than sticking to the typical hexagonal grid, introducing a meaningful
shift in both the x and y directions presents an opportunity for an
improved 2D model. Therefore, investigating this shift in the hexagonal
grid is an important parameter to consider.

As shown in Figure~\ref{fig-scurveshifthexgrids}, the shifting
influences the distribution of points and number of non-empty bins,
impacting the resulting 2D model. According to
\textbf{?@fig-diagnosticpltScurvehexbins}, the 2D model with a total of
\(144\) bins applied to S-curve UMAP data does not require any shifting
because the lowest MSE occurs when no shift is introduced.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Hexagonal binning involves tessellating the \(xy\) plane over the set
defined by the range of \(x\) and \(y\) \citep{Dan2023}. Therefore, the
starting point of the hexagonal grid is important parameter to consider.
Having different starting point results in shifting the hexagonal grid
and bin centroids (see Figure~\ref{fig-scurveshifthexgridsexp}). With a
specific total number of bins (which corresponds to a specific range
along the x and y axes), it's essential to explore how different
starting points affect the model's performance (see
Figure~\ref{fig-mseScurvestartpoint}). This is because different
starting points result in varying distributions of non-empty bins (see
Figure~\ref{fig-scurveshifthexgrids}), impacting the model.
